Human capital mediates natural selection in contemporary humans

### 2022-01-03 why-natural-selection.Rmd
Separate out parent weights from age/qual weights. Rewrite PCs section in appendix based on new results.

```{r}
drake::loadd(res_pcs)
n_regs <- as.double(nrow(res_pcs))
prop_sig <- res_pcs %>% 
      group_by(dep.var) %>% 
      summarize(sig = sum(p.value <= 0.05/nrow(res_pcs))) %>% 
      pull(sig, name = dep.var)
```

To get a further insight into this we regress *n siblings* and *n children*
on individual principal components. As Figure \@ref(fig:plot-pc-regs)
shows, effects are larger and more significant in siblings regressions.
`r prop_sig[["N siblings"]]` principal components significantly
predicted number of siblings, while only `r prop_sig[["N children"]]`
significantly predicted number of children.

```{r plot-pc-regs, fig.cap = "Selection effects of 100 principal components of genetic data. Absolute effect sizes are plotted. Each dot represents one bivariate regression. Points are jittered on the Y axis.", fig.height = 2}

res_pcs %>% 
      mutate(
        estimate = abs(estimate),
        dep.var  = fct_relevel(dep.var, "N children")
      ) %>% 
      rename(p = p.value) %>% 
      ggplot(aes(estimate, dep.var, colour = p < 0.05/{{n_regs}})) + 
        geom_jitter(height = 0.15, width = 0, alpha = 0.8) + 
        scale_x_log10(labels = scales::label_number(accuracy = 0.0001)) +
        labs(x = "Effect size (log scale)", y = "") + 
        pval_scale(aesthetics = "colour")

>>>>

To get a further insight into this we regress *n siblings* and *n children*
on individual principal components. Figure \@ref(fig:plot-pc-regs)
shows the results. Labels show the top principal components. These
have larger effect sizes in siblings regressions. One possibility is that 
the parents' generation was less geographically mobile, and so geographic
patterns of childrearing were more correlated with principal components, which
partly capture the location of people's ancestors.

```{r plot-pc-regs, fig.cap = "Selection effects of 100 principal components of genetic data. Each dot represents one bivariate regression. Absolute effect sizes are plotted. Points are jittered on the Y axis. Top principal components are labelled."}

drake::loadd(res_pcs)
n_regs <- as.double(nrow(res_pcs))

pj <- position_jitter(height = 0.15, width = 0, seed = 12345)

res_pcs %>% 
      mutate(
        estimate = abs(estimate),
        dep.var  = fct_relevel(dep.var, "N children"),
        top_pcs  = ifelse(as.numeric(pc_name) <= 5, term, "")
      ) %>% 
      rename(p = p.value) %>% 
      ggplot(aes(estimate, dep.var, colour = p < 0.05/{{n_regs}})) + 
        geom_point(alpha = 0.8, position = pj) +
        geom_text(aes(estimate, dep.var, label = top_pcs), position = pj, 
                    hjust = "right", color = "black", size = 3) +
        scale_x_log10(labels = scales::label_number(accuracy = 0.0001)) +
        labs(x = "Effect size (log scale)", y = "") + 
        pval_scale(aesthetics = "colour")
